---
title: "Article-code"
output: html_document
date: '2023-01-22'
------------

#Update packages:
```{r}
install.packages("libstableR")
install.packages("libstableR")
install.packages("cubature")
install.packages("alphastable")
install.packages("invgamma")
install.packages("LaplacesDemon")
install.packages("libstableR")
install.packages("libstable4u")
library("lubridate")
library("magrittr")
library("mltest")
library(evmix)
library(nprobust)
library(BNPdensity)
```
#LOGARITHMIC MOMENTS METHODS
#Here we estimate the characteristic esposant, asymmetry and dispersion:
#We use the steps of Kuruoglu's paper:
```{r}
set.seed(1235)
X=stabledist::rstable(1200,1.9,0.5,1,3,pm=1)
# We estime alpha:
X_2k=X[2*(1:600)]
X_2k_1=X[2*(1:600)-1]
X_k_S = log(abs(X_2k - X_2k_1))
L_2_S=var(X_k_S)
al=(L_2_S/(pi^2 /6) -0.5)**(-0.5)

#We estime beta:
X_3k=X[3*(1:400)]
X_3k_1=X[3*(1:400)-1]
X_3k_2=X[3*(1:400)-2]
X_k_C=log(abs(X_3k + X_3k_1 -2*X_3k_2))
L_2_C=var(X_k_C)
theta_abs=(((pi**2)/12 - L_2_C)*(al**2) + (pi**2)/6)**(0.5)
beta=(tan(theta_abs)/tan(al*pi/2))* (2+2**al)/(2-2**al)
#We estimate the scale paramter :
L_1=mean(X_k_C)
gamma=cos(theta_abs)*exp((L_1+0.57721566)*al -0.57721566)*(1/(2+2**al))
print(paste("alpha=",al,"beta=",beta,"gamma=",gamma,"omega=",mean(X)))
```

#Estimation by characteristic function method:
#Here we estimate the four parameters of the alpha-stable law for parameterization 0:
#For initialisation: we use McCulloch's method, with the command #stable_fit_init
```{r}
#Estimation byempiricaal characteristic function
ecf.fn <- function(x,u) {
  g <- rep(0.0,length(u))
  h <- rep(0.0,length(u))
  for (i in 1:length(x)) {
    for (j in 1:length(u)) {
      g[j] <- g[j]+cos(u[j]*x[i])
      h[j] <- h[j]+sin(u[j]*x[i])
    }
  }
  g <- g/length(x)
  h <- h/length(x)
  g <- pmax(exp(-2),g)
  #have shown that set the limitation improve the estimation.
  yr <- sqrt(g^2+h^2)
  yi <- atan2(h,g)
  
  return(list("yr" = yr,"yi" = yi))
}
#Estimation par noyau gaussien:
N_gaussien<-function(z){
  return((1/sqrt(2*pi))*exp(-0.5*z^2))
}
Re<-function(r,u,x,bn){
  cos(u*r)*N_gaussien((r-x)/bn)
}
Int_Re<-function(u,x,bn){
  integrate(Re,lower=-Inf,upper=Inf,u=u,x=x,bn=bn,subdivisions = 100)$value
}
Im<-function(r,u,x,bn){
  sin(u*r)*N_gaussien((r-x)/bn)
}
Int_Im<-function(u,x,bn){
  integrate(Im,lower=-Inf,upper=Inf,u=u,x=x,bn=bn,subdivisions = 100)$value
}

ecf.fn1 <- function(x,u) {
  g <- rep(0.0,length(u))
  h <- rep(0.0,length(u))
  bn=bw.nrd0(x)
  for (i in 1:length(x)) {
    for (j in 1:length(u)) {
      g[j] <- g[j]+Int_Re(u[j],x[i],bn)
      h[j] <- h[j]+Int_Im(u[j],x[i],bn)
    }
  }
  g <- g/(length(x)*bn)
  h <- h/(length(x)*bn)
  yr <- sqrt(g^2+h^2)
  yi <- atan2(h,g)
  
  return(list("yr" = yr,"yi" = yi))
}

eta0 <- function(u, alpha, gamma, eps=0.05){
  if( abs(alpha-1) < eps){
    y <- (2/pi)*u*log(gamma*abs(u))
    y[u==0] <- 0.0
  } else {
    y <- tan(pi*alpha/2)*sign(u)*((abs(gamma*u)-abs(gamma*u)^alpha)/(gamma^alpha))
  }
  return(y)
}

CDF<-function(x,u){
  gamma0=stable_fit_init(x)[3]
  delta0=stable_fit_init(x)[4]
  x=(x-delta0)/gamma0
  y1 <- ecf.fn(x,u)[[1]]
  z1 <- log(-log(y1))
  v1 <- log(abs(u))
  a1 <- lm(z1~v1)
  alpha1 <- a1$coef[2]
  if (alpha1>= 1){
    x1<- ecf.fn1(x,u)
    y1 <- x1[[1]]
    z1 <- log(-log(y1))
    v1 <- log(abs(u))
    a1 <- lm(z1~v1)
    alpha1 <- a1$coef[2]
    if (alpha1>2){alpha1=2}
    if (alpha1<0){alpha1=0.1}
    temp <- a1$coef[1]
    gamma1 <- exp(temp/alpha1)
    #y3 <- x1[[2]]
    #v3 <- -gamma1^alpha1*eta0(u,alpha1,gamma1)
    #a3 <- lm(y3~0+v3+u)
    #beta1 <- a3$coef[1]
    #delta1<-a3$coef[2]
    #if (beta1>1){beta1=1}
    #if (beta1< -1){beta1=-1}
  }
  if (alpha1<1){
    temp <- a1$coef[1]
    gamma1 <- exp(temp/alpha1)
    y3 <- ecf.fn(x,u)[[2]]
    v3 <- -gamma1^alpha1*eta0(u,alpha1,gamma1)
    a3 <- lm(y3~0+v3+u)
    beta1 <- a3$coef[1]
    delta1<-a3$coef[2]
    if (beta1>1){beta1=1}
    if (beta1< -1){beta1=-1}
  }
  y3 <- ecf.fn(x,u)[[2]]
  v3 <- -gamma1^alpha1*eta0(u,alpha1,gamma1)
  a3 <- lm(y3~0+v3+u)
  beta1 <- a3$coef[1]
  delta1<-a3$coef[2]
  if (beta1>1){beta1=1}
  if (beta1< -1){beta1=-1}
  
  return(list(alpha=alpha1,beta=beta1,gamma=gamma1*gamma0,delta=delta1*gamma0+delta0))
}
```

#We test our CDF function which summarises the above method on data
#simulutions:

```{r}
u1=seq(0.1,1,length=10)
set.seed(1234)
X1=stabledist::rstable(2000,1.6,-0.8,5,12,pm=0)
#X1=stabledist::rstable(2000,0.8,0.8,3,-12,pm=0)
CDF(X1,u1)
```
#Maximum likelihood approximation method :
#Here we use the optim command to maximise the log-likelihood:
```{r}
L_stable<-function(param,obs){
  a1=param[1]
  b1=param[2]
  d1=param[3]
  o1=param[4]
  -sum(log(stable_pdf(x=obs,pars=c(a1,b1,d1,o1))))
}
Max_vrai<-function(x){
  tryCatch(
    {
      E_stable=optim(stable_fit_init(x),L_stable,obs=x)
      alpha=E_stable$par[1]
      beta=E_stable$par[2]
      gamma=E_stable$par[3]
      delta=E_stable$par[4]
    },
    error=function(cond){
      invisible()
    }
  )
  
  return(list(alpha=alpha,beta=beta,gamma=gamma,delta=delta))
}

```
#We test our method on simulated data
```{r}
set.seed(1234)
X1=stabledist::rstable(2000,1.6,-0.8,5,12,pm=0)
#X1=stabledist::rstable(2000,0.8,0.8,3,-12,pm=0)
Max_vrai(X1)
```
# Maximum likelihood approximation method part two:
#Here, we use the scores given the partial derivatives of the density with respect to each parameter.
#to each parameter depend on these special functions:
```{r}
g_1_plus_alpha_tild<-function(r,x){
  sin(((x-omega)/delta)*r - beta*tan(pi*alpha/2)*(r**alpha) )*(r**alpha) * exp(-(r**alpha))
}

area1<-function(x){integrate(g_1_plus_alpha_tild,lower=0,upper=Inf,subdivisions = 10000,x=x)$value}
int_g_1_plus_alpha_tild <- Vectorize(area1)


h_1_plus_alpha_tild<-function(r,x){
  sin(((x-omega)/delta) * r -beta*tan(pi*alpha/2)*(r**alpha))*(log(r))*(r**alpha)*exp(-(r**alpha))
}
area2<-function(x){integrate(h_1_plus_alpha_tild,lower=0,upper=Inf,x=x,subdivisions=10000)$value}
int_h_1_plus_alpha_tild<- Vectorize(area2)

h_1_plus_alpha<-function(r,x){
  cos(((x-omega)/delta) * r -beta*tan(pi*alpha/2)*(r**alpha))*(log(r))*(r**alpha)*exp(-(r**alpha))
}
area3<-function(x){integrate(h_1_plus_alpha,lower=0,upper=Inf,x=x,subdivisions = 10000)$value}
int_h_1_plus_alpha<-Vectorize(area3)


g_1<-function(r,x){
  cos(((x-omega)/delta) *r - beta*tan(pi*alpha/2)*(r**alpha)) * exp(-(r**alpha))
}

area4<-function(x){integrate(g_1,lower=0,upper=Inf,x=x,subdivisions = 10000)$value}
int_g_1<-Vectorize(area4)


g_1_tild<-function(r,x){
  sin(((x-omega)/delta)*r - beta*tan(pi*alpha/2)*(r**alpha)) * exp(-(r**alpha))
}
area5<-function(x){integrate(g_1_tild,lower=0,upper=Inf,x=x,subdivisions = 10000)$value}
int_g_1_tild<-Vectorize(area5)


g_2_tild<-function(r,x){
  sin(((x-omega)/delta)*r - beta*tan(pi*alpha/2)*(r**alpha) )* r * exp(-(r**alpha))
}
area6<-function(x){integrate(g_2_tild,lower=0,upper=Inf,x=x,subdivisions = 10000)$value}
int_g_2_tild<-Vectorize(area6)
```

#Now we use the False-Position method to find the root of the log-likelihood.
#derivative of the log-likelihood with respect to each parameter:
#Apply directly to the simulated data:
```{r}
set.seed(1234)
X1=stabledist::rstable(2000,1.6,-0.8,5,12,pm=1)
#X1=stabledist::rstable(2000,0.8,0.8,3,-12,pm=1)
x=X1
E1=stable_fit_init(X1,parametrization = 1)
alpha1=E1[1]
beta1=E1[2]
delta1=E1[3]
omega1=E1[4]

L_alpha=c(alpha1-0.1,alpha1+0.1)
L_beta=c(beta1-0.1,beta1+0.1)
L_delta=c(delta1-0.1,delta1+0.1)
L_omega=c(omega1-0.5,omega1+0.5)

#We estimate alpha
alpha=L_alpha[length(L_alpha)]
beta=L_beta[length(L_beta)]
delta=L_delta[length(L_delta)]
omega=L_omega[length(L_omega)]
tryCatch(
  {
    grad_f_n=(1/(pi*delta))*((pi*beta/(2*(cos(pi*alpha/2)**2))) * int_g_1_plus_alpha_tild(x)
                         +beta*tan(pi*alpha/2) * int_h_1_plus_alpha_tild(x) - int_h_1_plus_alpha(x))
f_n=sum(grad_f_n)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))

alpha=L_alpha[length(L_alpha)-1]
beta=L_beta[length(L_beta)-1]
delta=L_delta[length(L_delta)-1]
omega=L_omega[length(L_omega)-1]
grad_f_n_1=(1/(pi*delta))*((pi*beta/(2*(cos(pi*alpha/2)**2))) * int_g_1_plus_alpha_tild(x)
                           +beta*tan(pi*alpha/2) * int_h_1_plus_alpha_tild(x) - int_h_1_plus_alpha(x))
f_n_1=sum(grad_f_n_1)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))
a_n=(f_n*L_alpha[length(L_alpha)-1]-f_n_1*L_alpha[length(L_alpha)])/(f_n-f_n_1)
L_alpha<-c(L_alpha,a_n)

# We estimate  beta
alpha=L_alpha[length(L_alpha)-1]
beta=L_beta[length(L_beta)]
delta=L_delta[length(L_delta)]
omega=L_omega[length(L_omega)]
grad_f_n=(tan(pi*alpha/2)/(pi*delta)) * int_g_1_plus_alpha_tild(x)
f_n=sum(grad_f_n)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))

alpha=L_alpha[length(L_alpha)-2]
beta=L_beta[length(L_beta)-1]
delta=L_delta[length(L_delta)-1]
omega=L_omega[length(L_omega)-1]
grad_f_n_1=(tan(pi*alpha/2)/(pi*delta)) * int_g_1_plus_alpha_tild(x)
f_n_1=sum(grad_f_n_1)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))
b_n=(f_n*L_beta[length(L_beta)-1]-f_n_1*L_beta[length(L_beta)])/(f_n-f_n_1)
L_beta<-c(L_beta,b_n)

# We estimate  delta
alpha=L_alpha[length(L_alpha)-1]
beta=L_beta[length(L_beta)-1]
delta=L_delta[length(L_delta)]
omega=L_omega[length(L_omega)]
grad_f_n=-(1/(pi*(delta)**2))*int_g_1(x)+((x-omega)/(pi*(delta)**3))*int_g_2_tild(x)
f_n=sum(grad_f_n)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))

alpha=L_alpha[length(L_alpha)-2]
beta=L_beta[length(L_beta)-2]
delta=L_delta[length(L_delta)-1]
omega=L_omega[length(L_omega)-1]
grad_f_n_1=-(1/(pi*(delta)**2))*int_g_1(x)+((x-omega)/(pi*(delta)**3))*int_g_2_tild(x)
f_n_1=sum(grad_f_n_1)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))
d_n=(f_n*L_delta[length(L_delta)-1]-f_n_1*L_delta[length(L_delta)])/(f_n-f_n_1)
L_delta<-c(L_delta,d_n)

# We estimate  omega
alpha=L_alpha[length(L_alpha)-1]
beta=L_beta[length(L_beta)-1]
delta=L_delta[length(L_delta)-1]
omega=L_omega[length(L_omega)]
grad_f_n=(1/(pi*(delta)**2))*int_g_2_tild(x)
f_n=sum(grad_f_n)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))

alpha=L_alpha[length(L_alpha)-2]
beta=L_beta[length(L_beta)-2]
delta=L_delta[length(L_delta)-2]
omega=L_omega[length(L_omega)-1]
grad_f_n_1=(1/(pi*(delta)**2))*int_g_2_tild(x)
f_n_1=sum(grad_f_n_1)/sum(stable_pdf(x,pars=c(alpha,beta,delta,omega),parametrization = 1))
o_n=(f_n*L_omega[length(L_omega)-1]-f_n_1*L_omega[length(L_omega)])/(f_n-f_n_1)
L_omega<-c(L_omega,o_n)
  },
 error=function(cond){
   invisible()
 }
)

print(paste("alpha=",a_n,"beta=",b_n,"gamma=",d_n,"omega=",o_n))
 
```
#Mixture estimation
#With simulated data
```{r}
w.true     = 0.6 
alpha1.true    = 1.2
beta1.true = 0.5   
delta1.true=1 
omega1.true=-4.25
alpha2.true=1.2
#beta2.true=0
beta2.true=-0.5
delta2.true=0.5
omega2.true=0.3
alpha.true=c(alpha1.true,alpha2.true)
beta.true=c(beta1.true,beta2.true)
delta.true=c(delta1.true,delta2.true)
omega.true=c(omega1.true,omega2.true)

xx.true = seq(-8,11,length=200)
yy.true = w.true*stable_pdf(xx.true,pars=c(alpha1.true,beta1.true,delta1.true,omega1.true)) + 
  (1-w.true)*stable_pdf(xx.true,pars=c(alpha2.true,beta2.true,delta2.true,omega2.true)) 
plot(xx.true, yy.true, type="l", xlab="x", ylab="True density", lwd=2)

set.seed(123)
oo=sample(1:2,1000,replace=T,prob=c(w.true,1-w.true))

lok=rep(1,1000)
for (i in 1:1000){
  lok[i]=stabledist::rstable(1,alpha = alpha.true[oo[i]],beta = beta.true[oo[i]],gamma=delta.true[oo[i]],delta=omega.true[oo[i]],pm=0)
}

```
#ECF is applied to the simulated data:
```{r}
CDF<-function(x,u){
  gamma0=stable_fit_init(x)[3]
  delta0=stable_fit_init(x)[4]
  x=(x-delta0)/gamma0
  y1 <- ecf.fn(x,u)[[1]]
  z1 <- log(-log(y1))
  v1 <- log(abs(u))
  a1 <- lm(z1~v1)
  alpha1 <- a1$coef[2]
  if (alpha1>2){alpha1=2}
  if (alpha1<0){alpha1=0.1}  
  temp <- a1$coef[1]
  gamma1 <- exp(temp/alpha1)
  y3 <- ecf.fn(x,u)[[2]]
  v3 <- -gamma1^alpha1*eta0(u,alpha1,gamma1)
  a3 <- lm(y3~0+v3+u)
  beta1 <- a3$coef[1]
  delta1<-a3$coef[2]
  if (beta1>1){beta1=1}
  if (beta1< -1){beta1=-1}
  
  return(list(alpha=alpha1,beta=beta1,gamma=gamma1*gamma0,delta=delta1*gamma0+delta0))
}

u1=seq(0.1,1,length=10)
set.seed(123)
a<-kmeans(lok,centers=2)$cluster
lok1<-CDF(lok[a==1],u1)
lok2<-CDF(lok[a==2],u1)
M_w=c(mean(a==1))
w=mean(a==1)
M_alpha1=c(lok1[[1]])
alpha1=lok1[[1]]
M_beta1=c(lok1[[2]])
beta1=lok1[[2]]
M_delta1=c(lok1[[3]])
delta1=lok1[[3]]
M_omega1=c(lok1[[4]])
omega1=lok1[[4]]
M_alpha2=c(lok2[[1]])
alpha2=lok2[[1]]
M_beta2=c(lok2[[2]])
beta2=lok2[[2]]
M_delta2=c(lok2[[3]])
delta2=lok2[[3]]
M_omega2=c(lok2[[4]])
omega2=lok2[[4]]
#M_cc=array(0, dim=c(100+1, 1000))
#M_cc[1,]=a
sw=TRUE
LV=-Inf
epsilon=10^(-2.5)
s=0

while(sw){
  #cc=M_cc[s,]
  cc = rep(0,1000)
  for(i in 1:1000){
    v = rep(0,2)
    v[1] = log(w) + log(stable_pdf(lok[i], pars=c(alpha1,beta1,delta1,omega1))) 
    v[2] = log(1-w) + log(stable_pdf(lok[i], pars=c(alpha2,beta2,delta2,omega2)))  
    v = exp(v - max(v))/sum(exp(v - max(v)))
    cc[i] = sample(1:2, 1, replace=TRUE, prob=v)
  }
  M_w<-c(M_w,mean(cc==1))
  w=mean(cc==1)
  
  L1<-CDF(lok[cc==1],u1)
  M_alpha1<-c(M_alpha1,L1[[1]])
  alpha1<-L1[[1]]
  M_beta1<-c(M_beta1,L1[[2]])
  beta1<-L1[[2]]
  M_delta1<-c(M_delta1,L1[[3]])
  delta1<-L1[[3]]
  M_omega1<-c(M_omega1,L1[[4]])
  omega1<-L1[[4]]
  
  
  L2<-CDF(lok[cc==2],u1)
  M_alpha2<-c(M_alpha2,L2[[1]])
  alpha2<-L2[[1]]
  M_beta2<-c(M_beta2,L2[[2]])
  beta2<-L2[[2]]
  M_delta2<-c(M_delta2,L2[[3]])
  delta2<-L2[[3]]
  M_omega2<-c(M_omega2,L2[[4]])
  omega2<-L2[[4]]
  
  LVn<- sum(log(w*stable_pdf(lok,pars=c(alpha1,beta1,delta1,omega1))
               +(1-w)*stable_pdf(lok,pars=c(alpha2,beta2,delta2,omega2))))
  if(abs(LVn-LV)/abs(LVn)<epsilon){
    sw=FALSE
  }
  LV=LVn
  s=s+1
  print(paste("s=",s, "log-V=",LVn))
}

xx = seq(-8,11,length=200)
yy = w*stable_pdf(xx,pars=c(alpha1,beta1,delta1,omega1)) + 
  (1-w)*stable_pdf(xx,pars=c(alpha2,beta2,delta2,omega2)) 

plot(xx, yy, type="l", ylim=c(0, max(c(yy,yy.true))), main="EM-ECF method", lwd=2, col="red", lty=2, xlab="x", ylab="Density")
lines(xx.true, yy.true, lwd=2)
legend(6,0.22,c("Truth","Estimate"),col=c("black","red"), lty=c(1,2), bty="n")

```

#On applique EM par maximum de vraisemblance
```{r}
set.seed(123)
a<-kmeans(lok,centers=2)$cluster
#lok1<-stable_fit_mle(lok[a==1])
#lok2<-stable_fit_mle(lok[a==2])
lok1<-Max_vrai(lok[a==1])
lok2<-Max_vrai(lok[a==2])
M_w=c(mean(a==1))
w=mean(a==1)
M_alpha1=c(lok1[[1]])
alpha1=lok1[[1]]
M_beta1=c(lok1[[2]])
beta1=lok1[[2]]
M_delta1=c(lok1[[3]])
delta1=lok1[[3]]
M_omega1=c(lok1[[4]])
omega1=lok1[[4]]
M_alpha2=c(lok2[[1]])
alpha2=lok2[[1]]
M_beta2=c(lok2[[2]])
beta2=lok2[[2]]
M_delta2=c(lok2[[3]])
delta2=lok2[[3]]
M_omega2=c(lok2[[4]])
omega2=lok2[[4]]
#M_cc=array(0, dim=c(100+1, 1000))
#M_cc[1,]=a
sw=TRUE
LV=-Inf
epsilon=10^(-3.5)
s=0

while(sw){
  #cc=M_cc[s,]
  cc = rep(0,1000)
  for(i in 1:1000){
    v = rep(0,2)
    v[1] = log(w) + log(stable_pdf(lok[i], pars=c(alpha1,beta1,delta1,omega1))) 
    v[2] = log(1-w) + log(stable_pdf(lok[i], pars=c(alpha2,beta2,delta2,omega2)))  
    v = exp(v - max(v))/sum(exp(v - max(v)))
    cc[i] = sample(1:2, 1, replace=TRUE, prob=v)
  }
  M_w<-c(M_w,mean(cc==1))
  w=mean(cc==1)
  
  #L1<-stable_fit_mle(lok[cc==1])
  L1<-Max_vrai(lok[cc==1])
  M_alpha1<-c(M_alpha1,L1[[1]])
  alpha1<-L1[[1]]
  M_beta1<-c(M_beta1,L1[[2]])
  beta1<-L1[[2]]
  M_delta1<-c(M_delta1,L1[[3]])
  delta1<-L1[[3]]
  M_omega1<-c(M_omega1,L1[[4]])
  omega1<-L1[[4]]
  
  
  #L2<-stable_fit_mle(lok[cc==2])
  L2<-Max_vrai(lok[cc==2])
  M_alpha2<-c(M_alpha2,L2[[1]])
  alpha2<-L2[[1]]
  M_beta2<-c(M_beta2,L2[[2]])
  beta2<-L2[[2]]
  M_delta2<-c(M_delta2,L2[[3]])
  delta2<-L2[[3]]
  M_omega2<-c(M_omega2,L2[[4]])
  omega2<-L2[[4]]
  
  LVn<- sum(log(w*stable_pdf(lok,pars=c(alpha1,beta1,delta1,omega1))
                +(1-w)*stable_pdf(lok,pars=c(alpha2,beta2,delta2,omega2))))
  if(abs(LVn-LV)/abs(LVn)<epsilon){
    sw=FALSE
  }
  LV=LVn
  s=s+1
  print(paste("s=",s,LVn))
}

xx = seq(-8,11,length=200)
yy = w*stable_pdf(xx,pars=c(alpha1,beta1,delta1,omega1)) + 
  (1-w)*stable_pdf(xx,pars=c(alpha2,beta2,delta2,omega2)) 

plot(xx, yy, type="l", ylim=c(0, max(c(yy,yy.true))), main="EM-ML method", lwd=2, col="red", lty=2, xlab="x", ylab="Density")
lines(xx.true, yy.true, lwd=2)
legend(6,0.22,c("Truth","Estimate"),col=c("black","red"), lty=c(1,2), bty="n")

```
# We apply the MCMC method below:
```{r}
u1=seq(0.1,1,length=10)
set.seed(123)
a<-kmeans(lok,centers=2)$cluster
lok1<-CDF(lok[a==1],u1)
lok2<-CDF(lok[a==2],u1)
M2_w1=c(mean(a==1))
w1=mean(a==1)
M2_w2=c(mean(a==2))
w2=mean(a==2)
M2_alpha1=c(lok1[[1]])
alpha1=lok1[[1]]
M2_beta1=c(lok1[[2]])
beta1=lok1[[2]]
M2_delta1=c(lok1[[3]])
delta1=lok1[[3]]
M2_omega1=c(lok1[[4]])
omega1=lok1[[4]]
M2_alpha2=c(lok2[[1]])
alpha2=lok2[[1]]
M2_beta2=c(lok2[[2]])
beta2=lok2[[2]]
M2_delta2=c(lok2[[3]])
delta2=lok2[[3]]
M2_omega2=c(lok2[[4]])
omega2=lok2[[4]]
n=1000
k=2
M2_cc=array(0, dim=c(rrr+1, n))
M2_cc[1,]=a

aa=c(1,1)
eta=0
tau=5
dd=1
qq=1


# Number of iterations of the sampler
rrr   = 300
#burn  = 1000

# MCMC iterations
for(s in 1:rrr){
  cc=M2_cc[s,]
  # Sample the weights
  w = rdirichlet(1, alpha=c(aa[1] + sum(cc==1), aa[2] + sum(cc==2)))
  w1=w[1]
  M2_w1<-c(M2_w1,w1)
  w2=w[2]
  M2_w2<-c(M2_w2,w2)
  
  
  #Metropolis-hasting algorithm:
  
  logique1=TRUE
  while (logique1) {
    alpha1_star=rnorm(1,mean=M2_alpha1[s],sd=0.1)
    if(alpha1_star>0 & alpha1_star<=2){logique1=FALSE}
  }
  logique2=TRUE
  while (logique2) {
    alpha2_star=rnorm(1,mean=M2_alpha2[s],sd=0.1)
    if(alpha2_star>0 & alpha2_star<=2){logique2=FALSE}
  }
  logique3=TRUE
  while (logique3) {
    beta1_star=rnorm(1,mean=M2_beta1[s],sd=0.1)
    if (beta1_star<=1 & beta1_star>=-1){logique3=FALSE}
  }
  logique4=TRUE
  while (logique4) {
    beta2_star=rnorm(1,mean=M2_beta2[s],sd=0.1)
    if (beta2_star<=1 & beta2_star>=-1){logique4=FALSE}
  }
  logique5=TRUE
  while (logique5) {
    delta1_star=rnorm(1,mean=M2_delta1[s],sd=0.1)
    if (delta1_star>0){logique5=FALSE}
  }
  logique6=TRUE
  while (logique6) {
    delta2_star=rnorm(1,mean=M2_delta2[s],sd=0.1)
    if (delta2_star>0){logique6=FALSE}
  }
  logique7=TRUE
  while (logique7){
    omega1_star=rnorm(1,mean=M2_omega1[s],sd=0.1)
    omega2_star=rnorm(1,mean=M2_omega2[s],sd=0.1)
    if (omega2_star>omega1_star){logique7=FALSE}
  }

densite1=(prod((10^1)*stable_pdf(lok[cc==1],pars=c(alpha1_star,beta1_star,delta1_star,omega1_star)))*dinvgamma(delta1_star,dd,qq)*dnorm(omega1_star,eta,tau))/(prod((10^1)*stable_pdf(lok[cc==1],pars=c(M2_alpha1[s],M2_beta1[s],M2_delta1[s],M2_omega1[s])))*dinvgamma(M2_delta1[s],dd,qq)*dnorm(M2_omega1[s],eta,tau))
  if (runif(1)<densite1){
    M2_alpha1[s+1]<-alpha1_star
    M2_beta1[s+1]<-beta1_star
    M2_delta1[s+1]<-delta1_star
    M2_omega1[s+1]<-omega1_star
  }
  else{
    M2_alpha1[s+1]<-M2_alpha1[s]
    M2_beta1[s+1]<-M2_beta1[s]
    M2_delta1[s+1]<-M2_delta1[s]
    M2_omega1[s+1]<-M2_omega1[s]
  }
  alpha1=M2_alpha1[s+1]
  beta1=M2_beta1[s+1]
  delta1=M2_delta1[s+1]
  omega1=M2_omega1[s+1]
  
densite2=(prod((10^1)*stable_pdf(lok[cc==2],pars=c(alpha2_star,beta2_star,delta2_star,omega2_star)))*dinvgamma(delta2_star,dd,qq)*dnorm(omega2_star,eta,tau))/(prod((10^1)*stable_pdf(lok[cc==2],pars=c(M2_alpha2[s],M2_beta2[s],M2_delta2[s],M2_omega2[s])))*dinvgamma(M2_delta2[s],dd,qq)*dnorm(M2_omega2[s],eta,tau))
if (runif(1)<densite2){
    M2_alpha2[s+1]<-alpha2_star
    M2_beta2[s+1]<-beta2_star
    M2_delta2[s+1]<-delta2_star
    M2_omega2[s+1]<-omega2_star
  }
  else{
    M2_alpha2[s+1]<-M2_alpha2[s]
    M2_beta2[s+1]<-M2_beta2[s]
    M2_delta2[s+1]<-M2_delta2[s]
    M2_omega2[s+1]<-M2_omega2[s]
  }
  alpha2=M2_alpha2[s+1]
  beta2=M2_beta2[s+1]
  delta2=M2_delta2[s+1]
  omega2=M2_omega2[s+1]
  
  
# Sample the indicators
  cc = rep(0,n)
  for(i in 1:n){
    v = rep(0,2)
    v[1] = log(w1) + log(stable_pdf(lok[i], pars=c(alpha1,beta1,delta1,omega1)))  #Compute the log of the weights
    v[2] = log(w2) + log(stable_pdf(lok[i], pars=c(alpha2,beta2,delta2,omega2)))  #Compute the log of the weights
    v = exp(v - max(v))/sum(exp(v - max(v)))
    cc[i] = sample(1:2, 1, replace=TRUE, prob=v)
  }
  M2_cc[s+1,]=cc
  
  print(paste('s=', s))
}

xx = seq(-8,11,length=200)
yy = mean(M2_w1[20:301])*stable_pdf(xx,pars=c(mean(M2_alpha1[20:301]),mean(M2_beta1[20:301]),mean(M2_delta1[20:301]),mean(M2_omega1[20:301]))) + 
  (1-mean(M2_w1[20:301]))*stable_pdf(xx,pars=c(mean(M2_alpha2[20:301]),mean(M2_beta2[20:301]),mean(M2_delta2[20:301]),mean(M2_omega2[20:301]))) 

plot(xx, yy, type="l", ylim=c(0, max(c(yy,yy.true))), main="MCMC method", lwd=2, col="red", lty=2, xlab="x", ylab="Density")
lines(xx.true, yy.true, lwd=2)
legend(6,0.22,c("Truth","Estimate"),col=c("black","red"), lty=c(1,2), bty="n")

```
#Now we move on to the application part on the serial interval:
#We start by calculating this interval:

```{r}
data=read.table("DONNEE.csv",sep=";",dec=".",header = T)
data$x.lb <- strptime(as.character(data$x.lb), "%d/%m/%Y")
data$x.lb <- format(data$x.lb, "%Y-%m-%d")
data$x.lb <- time_length(interval(start = ymd("2020-01-01"), end = data$x.lb), unit = "days")

data$x.ub <- strptime(as.character(data$x.ub), "%d/%m/%Y")
data$x.ub <- format(data$x.ub, "%Y-%m-%d")
data$x.ub <- time_length(interval(start = ymd("2020-01-01"), end = data$x.ub), unit = "days")

data$y <- strptime(as.character(data$y), "%d/%m/%Y")
data$y <- format(data$y, "%Y-%m-%d")
data$y <- time_length(interval(start = ymd("2020-01-01"), end = data$y), unit = "days")
S=data$y - (data$x.ub + data$x.lb)/2
data$SI<-S
hist(S, freq=F,main="Histogramme de l'intervalle sérial")
```
#The mixture model is applied to the serial interval using EM-ML:
```{r}
set.seed(134)
a<-kmeans(S,centers=2)$cluster
S1<-stable_fit_mle(S[a==1])
S2<-stable_fit_mle(S[a==2])
M_w=c(mean(a==1))
w=mean(a==1)
M_alpha1=c(S1[[1]])
alpha1=S1[[1]]
M_beta1=c(S1[[2]])
beta1=S1[[2]]
M_delta1=c(S1[[3]])
delta1=S1[[3]]
M_omega1=c(S1[[4]])
omega1=S1[[4]]
M_alpha2=c(S2[[1]])
alpha2=S2[[1]]
M_beta2=c(S2[[2]])
beta2=S2[[2]]
M_delta2=c(S2[[3]])
delta2=S2[[3]]
M_omega2=c(S2[[4]])
omega2=S2[[4]]
sw=TRUE
LV=-Inf
epsilon=10^(-5)
s=0

while(sw){
  cc = rep(0,77)
  for(i in 1:77){
    v = rep(0,2)
    v[1] = log(w) + log(stable_pdf(S[i], pars=c(alpha1,beta1,delta1,omega1)))  
    v[2] = log(1-w) + log(stable_pdf(S[i], pars=c(alpha2,beta2,delta2,omega2))) 
    v = exp(v - max(v))/sum(exp(v - max(v)))
    cc[i] = sample(1:2, 1, replace=TRUE, prob=v)
  }
  M_w<-c(M_w,mean(cc==1))
  w=mean(cc==1)
  
  L1<-stable_fit_mle(S[cc==1])
  M_alpha1<-c(M_alpha1,L1[[1]])
  alpha1<-L1[[1]]
  M_beta1<-c(M_beta1,L1[[2]])
  beta1<-L1[[2]]
  M_delta1<-c(M_delta1,L1[[3]])
  delta1<-L1[[3]]
  M_omega1<-c(M_omega1,L1[[4]])
  omega1<-L1[[4]]
  
  
  L2<-stable_fit_mle(S[cc==2])
  M_alpha2<-c(M_alpha2,L2[[1]])
  alpha2<-L2[[1]]
  M_beta2<-c(M_beta2,L2[[2]])
  beta2<-L2[[2]]
  M_delta2<-c(M_delta2,L2[[3]])
  delta2<-L2[[3]]
  M_omega2<-c(M_omega2,L2[[4]])
  omega2<-L2[[4]]
  
  LVn<- sum(log(w*stable_pdf(S,pars=c(alpha1,beta1,delta1,omega1))
                +(1-w)*stable_pdf(S,pars=c(alpha2,beta2,delta2,omega2))))
  if(abs(LVn-LV)/abs(LVn)<epsilon){
    sw=FALSE
  }
  LV=LVn
  s=s+1
  print(paste("s=",s,LVn))
}

X1<-function(x,alpha1,beta1,delta1,omega1,alpha2,beta2,delta2,omega2){
  return(w*stable_pdf(x,pars=c(alpha1,beta1,delta1,omega1))+(1-w)*stable_pdf(x,pars = c(alpha2,beta2,delta2,omega2)))
}

x=S
hist(S,freq=F,main="Mixture of alpha-stable for serial interval")
curve(X1(x,alpha1,beta1,delta1,omega1,alpha2,beta2,delta2,omega2),type="l",add=T,col="red",lwd=2)

```

